Responses to Reviews

### 2016-07-10 RMS/responses.tex
complete responses to reviewer 2

@@

[Page 4] line 45:
Why is a period of sort Nat? Shouldn't it be Counter?

@@

>>>>

Thanks for pointing this out. Actually some of the timed operators are
used in Section V.A when describing the properties we verify. This
little problem is addressed now. We now only mention the necessary
timed operators which will be used, and also add explanations when
using them in Section V.A.

@@

[Page 4] line 45: 
Why is a period of sort \verb|Nat|? Shouldn't it be \verb|Counter|?

@@

This is a good question!

In our model, as we discuss in Section IV.A, a \verb|Counter| contains
two elements: the execution time (the time how long a task has been
executing for) and the computation requirement (the time how long a
task should execute for). A \verb|Counter| is some kind of
``dynamic''. It is like a countdown timer to complete the execution of
a task. Different from \verb|Counter|, a period is a ``static''
property of a task. Therefore, a period is modeled as a term of sort
\verb|Nat| instead of \verb|Counter|.

On the other hand, a period can also be modeled as a \verb|Counter|.
Then it becomes a countdown timer to trigger an execution request of
the task, while the execution requests are currently triggered by the
periodic interrupts in our model.

Both ways to model periods are feasible. We choose the former since
its behaviors are more faithful to the real implementation we model
and verify.
